Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-20 ms.tex
working2

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ \\
\hline
$(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
\hline
$    10^{ 6 }$ & 300 & 0.8 & $>$ & $ 1.3 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ & No \\
$    10^{ 6 }$ & 600 & 0.8 & $>$ & $ 2.2 \times 10^{ -6 }$ & $ 8. 10^{ 3 }$ & No \\
$    10^{ 6 }$ & 1200 & 0.8 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ & No \\
$    10^{ 7 }$ & 300 & 0.8 & 100 & $ 1.3 \times 10^{ -4 }$ & 6.5 & No \\
$    10^{ 7 }$ & 600 & 0.8 & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ & No \\
$    10^{ 7 }$ & 1200 & 0.8 & $>$ & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ & No \\
$    10^{ 8 }$ & 300 & 0.8 & 100 & $ 6.6 \times 10^{ -4 }$ & 1.4 & Yes \\
$    10^{ 8 }$ & 600 & 0.8 & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.8 & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ & No \\
$    10^{ 7 }$ & 300 & 0.8 & 50 & $ 7.9 \times 10^{ -5 }$ & 12 & No \\
$    10^{ 7 }$ & 300 & 0.8 & 200 & $ 1.2 \times 10^{ -4 }$ & 4.7 & Yes \\
$    10^{ 7 }$ & 300 & 0.8 & 400 & $ 3.6 \times 10^{ -4 }$ & 1.2 & Yes \\
$    10^{ 8 }$ & 300 & 0.8 & 50 & $ 3.3 \times 10^{ -4 }$ & 4.6 & Yes\\
$10^{8}\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & Yes & \\
$    10^{ 8 }$ & 300 & 0.8 & 200 & $ 1.4 \times 10^{ -3 }$ & 0.43 & Yes \\
$    10^{ 6 }$ & 1200 & 0.1 & $>$ & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ & No \\
$    10^{ 7 }$ & 1200 & 0.1 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2. 10^{ 4 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3. 10^{ 4 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 400 & $ 1.2 \times 10^{ -3 }$ & 4.6 & Yes \\
\hline
\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  $^{(e)}$ Is solution thermally unstable?
$\dagger$Calculated including radiative cooling, assuming $\eta =
0.04$.  {\bf  BDM: (3) make sure all combinations of vw and mbh
  are included. AG: Realized that the solution I ran earlier, with
  cooling was actually a solution that would be thermally unstable
  according to our thermal instability. I am worried that this
  solution may not be representative due to the small break radius.}
\end{tablenotes}
\end{minipage}
\end{threeparttable}

>>>>

\begin{table*}
\begin{threeparttable}
%\centering
\begin{minipage}{18cm}
\caption{Summary of Numerical Solutions}
\begin{tabular}{lccccccccccccc}
\hline
{$M_{\bullet}$} & {$v_{w}$} & {$\Gamma^{(a)}$} & {$r_b^{(b)}$} &
{$\left(\frac{\dot{M}}{\dot{M}_{\rm edd}}\frac{0.04}{\eta}\right)_{r_{s}}^{(c)}$} & {$\left(\frac{t_{\rm cool}}{t_{\rm ff}}\frac{0.04}{\eta}\right)_{r_s}^{(d)}$} & TI?$^{(e)}$ \\
\hline
$(M_{\odot})$ & (km s$^{-1})$ & & (pc) & & &  & \\
\hline
$    10^{ 6 }$ & 300 & 0.8 & $>$ & $ 1.3 \times 10^{ -5 }$ & $ 1.2 \times 10^{ 2 }$ & No \\
$    10^{ 6 }$ & 600 & 0.8 & $>$ & $ 2.2 \times 10^{ -6 }$ & $ 8. 10^{ 3 }$ & No \\
$    10^{ 6 }$ & 1200 & 0.8 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 3.7 \times 10^{ 5 }$ & No \\
$    10^{ 7 }$ & 300 & 0.8 & 100 & $ 1.3 \times 10^{ -4 }$ & 6.5 & No \\
$    10^{ 7 }$ & 600 & 0.8 & 100 & $ 7.2 \times 10^{ -6 }$ & $ 2.4 \times 10^{ 3 }$ & No \\
$    10^{ 7 }$ & 1200 & 0.8 & $>$ & $ 1.3 \times 10^{ -6 }$ & $ 1.2 \times 10^{ 5 }$ & No \\
$    10^{ 8 }$ & 300 & 0.8 & 100 & $ 6.6 \times 10^{ -4 }$ & 1.4 & Yes \\
$    10^{ 8 }$ & 600 & 0.8 & 100 & $ 2.9 \times 10^{ -5 }$ & $ 5.3 \times 10^{ 2 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.8 & 100 & $ 4.0 \times 10^{ -6 }$ & $ 3.8 \times 10^{ 4 }$ & No \\
$    10^{ 7 }$ & 300 & 0.8 & 50 & $ 7.9 \times 10^{ -5 }$ & 12 & No \\
$    10^{ 7 }$ & 300 & 0.8 & 200 & $ 1.2 \times 10^{ -4 }$ & 4.7 & Yes \\
$    10^{ 7 }$ & 300 & 0.8 & 400 & $ 3.6 \times 10^{ -4 }$ & 1.2 & Yes \\
$    10^{ 8 }$ & 300 & 0.8 & 50 & $ 3.3 \times 10^{ -4 }$ & 4.6 & Yes\\
$10^{8}\dagger$ & 300 & 0.8 & 50 & $ 9.1 \times 10^{ -4 }$ & 5.6 & Yes & \\
$    10^{ 8 }$ & 300 & 0.8 & 200 & $ 1.4 \times 10^{ -3 }$ & 0.43 & Yes \\
$    10^{ 6 }$ & 1200 & 0.1 & $>$ & $ 5.9 \times 10^{ -8 }$ & $ 1.0 \times 10^{ 6 }$ & No \\
$    10^{ 7 }$ & 1200 & 0.1 & $>$ & $ 3.8 \times 10^{ -7 }$ & $ 1.4 \times 10^{ 5 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 100 & $ 2.4 \times 10^{ -6 }$ & $ 2. 10^{ 4 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 50 & $ 2.0 \times 10^{ -6 }$ & $ 3. 10^{ 4 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 200 & $ 4.2 \times 10^{ -6 }$ & $ 8.4 \times 10^{ 3 }$ & No \\
$    10^{ 8 }$ & 1200 & 0.1 & 400 & $ 1.2 \times 10^{ -3 }$ & 4.6 & Yes \\
\hline
\label{table:models}  
\end{tabular}
\begin{tablenotes}
\item $^{(a)}$ Inner power-law index of stellar Nuker profile.  $^{(b)}$
Break radius of stellar Nuker profile.  $^{(c)}$Accretion rate in
Eddington units, normalized to a stellar mass input parameter $\eta =
0.04$.  $^{(d)}$Ratio of cooling timescale to free-fall timescale at
stagnation radius.  Thermally unstable solutions are shown in bold text.  $^{(e)}$ Is solution thermally unstable?
$\dagger$Calculated including radiative cooling, assuming $\eta =
0.04$.  {\bf  BDM: (3) make sure all combinations of vw and mbh
  are included. AG: Realized that the solution I ran earlier, with
  cooling was actually a solution that would be thermally unstable
  according to our thermal instability. I am worried that this
  solution may not be representative due to the small break radius. BDM: change TI column to simply bolding tcool ratio in those cases which are thermally unstable.}
\end{tablenotes}
\end{minipage}
\end{threeparttable}
